---
title: "DataProductsWeek3Plotly"
author: "rmydeen"
date: "5/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
library(plotly)
library(data.table)
library(tidyr)
library(lubridate)
library(zoo)
library(openxlsx)
```

```{r echo=FALSE}
pickdate<-"2020-05-08"
xlsfile <-paste0("http://www.ecdc.europa.eu/sites/default/files/documents/COVID-19-geographic-disbtribution-worldwide-",pickdate,".xlsx")
URL<-paste0(xlsfile)
filename<-paste0("data\\covidcases_",pickdate,".xlsx")
if (!file.exists(filename))
  download.file(URL,
                destfile=filename,
                mode="wb")
colClass <- c("date","integer","integer","integer","integer","integer","character","character","chracter","integer","character")
covidcases<- read.xlsx(filename,sheet=1)
#Convert to Datesas.character(covidcases$dateRep)
covidcases$dateRep<-as.Date(covidcases$dateRep-25569, origin="1970-01-01")

df<-covidcases %>% group_by(date=dateRep,countryCode=countryterritoryCode) %>%
  summarise(cases=sum(cases),deaths=sum(deaths),population=mean(popData2018))

df_world<-covidcases %>% group_by(date=dateRep) %>%
  summarise(cases=sum(cases),deaths=sum(deaths),population=mean(popData2018))
#filter(countryCode=="IND") %>% 

total_cases <- sum(df$cases)
total_deaths <- sum(df$deaths)
```
## Summary
This web page depicts COVID-10 cases worldwide and India as of particular date
and plot world wide cases and deaths and India cases and deaths so far using plotly package in R programming.

## Covid-19 Cases & Deaths

This page contain two plots 1) Worldwide 2) India to depicts cases and deaths so far.

### World Case
 1.Worldwide (Figure 1)
 2.India (Figure 2)
```{r echo=FALSE}
fig <- plot_ly(df_world, x = ~date, y = ~cases, type = 'scatter', mode = 'lines+markers+text', color=I('blue'),name = 'Covid-19 World Cases')
fig <- fig %>% add_trace(y = ~deaths,color=I('red'), name = 'Deaths') %>% layout(title=paste0("Total Cases  World:",total_cases,",Deaths:",total_deaths," As of:",pickdate))
fig
```

### India Cases
```{r echo=FALSE}
df_india<-df  %>%filter(countryCode=="IND")
total_cases_ind <- sum(df_india$cases)
total_deaths_ind <- sum(df_india$deaths)
fig_ind <- plot_ly(df_india, x = ~date, y = ~cases, type = 'scatter', mode = 'lines+markers+text', color=I('Green'),name = 'Covid-19 India Cases')
fig_ind <- fig_ind %>% add_trace(y = ~deaths,color=I('Orange'), name = 'Deaths') %>% layout(title=paste0("Total India Cases:",total_cases_ind," Deaths:",total_deaths_ind," As of:",pickdate))
fig_ind

```
## Note
Code available in https://github.com/rabeekraja/DataProductsWk3

